---
title: "SOME TEST OF NORMALITY"
author: "Daniel James"
date: "`r Sys.Date()`"
output: html_document
---
  
  ```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "",
                      collapse = TRUE,
                      echo = TRUE,
                      error = TRUE, # do not interrupt in case of errors
                      message = FALSE,
                      warning = FALSE,
                      comma <- function(x) format(x, digits = 2, big.mark = ",")
)
## Load packages and prepare multicore process
library(pacman)
p_load(nortest)
p_load(moments)
p_load(tseries)
p_load(PoweR)
p_load(AMR)
p_load(tsoutliers)
p_load(lawstat)
p_load(dgof)
p_load(nortest)
```

# Normal Distribution

```{r simulate_Normal_Distribution, include=TRUE}
set.seed(1)
x <- rnorm(x, 0, 1)
```



## Jarque Bera test [jb] for NORMAL Dist

```{r normjb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,JarqueBeraTest(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera Test [rjb] for NORMAL Dist

```{r normrjb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,rjb.test(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kolmogorov – Smirnov test [ks] for NORMAL Dist

```{r normks, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,ks.test(rnorm(x),"pnorm"))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Shapiro-Francia method [sf] for NORMAL Dist

```{r normsf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,sf.test(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Chi-square goodness of fit for normality test [gf] for NORMAL Dist

```{r normgf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,PearsonTest(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```


## Shapiro- wilk test [sw] for NORMAL Dist

```{r normsw, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,shapiro.test(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Anderson-Darling test [AD] for NORMAL Dist


```{r normAD, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, ad.test(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Bonett-Serial test[BS] for NORMAL Dist

```{r normBS, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(factor(round(unlist(replicate(1000, 
                                      bonett.test(rnorm(x)))["p.value",]), 2) 
               != round(sqrt(2/pi),  2), levels = c(TRUE, FALSE)))))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera test [RJB] for NORMAL Dist

```{r normRJB, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, jarque.bera.test(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## D’Agostino- Pearson K2 test [DK] for NORMAL Dist

```{r normDK, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, agostino.test(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Skewness test for NORMAL Dist

```{r normSKEWNESS, include=TRUE}
skew.test <- function (x) {
  m3 <- sum((x-mean(x))^3)/length(x)
  s3 <- sqrt(var(x))^3
  skew <- m3/s3
  ses <- sqrt(6/length(x))
  totest <- skew/ses
  pt(totest,(length(x)-1))
  pval <- pt(totest,(length(x)-1))
  pval
}

out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, skew.test(rnorm(x))) < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kurtosis tes for NORMAL Dist

```{r normKURTOSIS, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)
  table(replicate(1000, kurtosis(rnorm(x)))-3 > 1)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Lilliefores (LL) Test for NORMAL Dist

```{r normLL, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, lillie.test(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Cramer–von Mises (CVM) test for NORMAL Dist

```{r normCVM, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, cvm.test(rnorm(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```
######################################################################################
# BETA DIST

```{r simulate_Beta_Distribution, include=TRUE}
set.seed(1)
x <- rbeta(x, shape1 = 2, shape2 = 8)
```

## Shapiro- wilk test [sw] for BETER Dist

```{r beter_SW_B, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,shapiro.test(rbeta(n = x, shape1 = 2, shape2 = 8)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Anderson-Darling test [AD] for BETER Dist

```{r beter_AD_B, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, ad.test(rbeta(n = x, shape1 = 2, shape2 = 8)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Bonett-Serial test[BS] for BETER Dist

```{r beter_BS_B, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(factor(round(unlist(replicate(1000, 
                                      bonett.test(rbeta(n = x, shape1 = 2, shape2 = 8)))["p.value",]), 2) 
               != round(sqrt(2/pi),  2), levels = c(TRUE, FALSE)))))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera test [RJB] for BETER Dist

```{r beter_RJB_B, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, jarque.bera.test(rbeta(n = x, shape1 = 2, shape2 = 8)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## D’Agostino- Pearson K2 test [DK] for BETER Dist
```{r beter_DA_B, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, agostino.test(rbeta(n = x, shape1 = 2, shape2 = 8)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Skewness test for BETER Dist

```{r beter_SKEWNESS_D, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)   table(factor(abs(unlist(replicate(1000, skewness(rbeta(n = x, shape1 = 2, shape2 = 8))))) > 2, levels = c(TRUE, FALSE)))))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kurtosis tes for BETER Dist

```{r beter_KURTOSIS_B, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)
  table(replicate(1000, kurtosis(rbeta(n = x, shape1 = 2, shape2 = 8)))-3 > 1)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Lilliefores (LL) Test for gamma for BETER Dist

```{r beter_LL_B, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, lillie.test(rbeta(n = x, shape1 = 2, shape2 = 8)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```


## Jarque Bera test [jb]  for BETER Dist

```{r beter_beter_jb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,JarqueBeraTest(rbeta(x, shape1 = 2, shape2 = 8)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera Test [rjb] for BETER Dist

```{r beter_rjb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,rjb.test(rbeta(x, shape1 = 2, shape2 = 8)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kolmogorov – Smirnov test [ks] for BETER Dist

```{r beter_ks, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,ks.test(rbeta(x, shape1 = 2, shape2 = 8),"pnorm"))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Shapiro-Francia method [sf] for BETER Dist

```{r beter_sf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,sf.test(rbeta(x, shape1 = 2, shape2 = 8)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Chi-square goodness of fit for normality test [gf] for BETER Dist

```{r beter_gf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,PearsonTest(rbeta(x, shape1 = 2, shape2 = 8)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```
##################################################################################################
```{r simulate_Gamma_Distribution, include=TRUE}
set.seed(1)
x <- rgamma(x, shape = 3, rate =0.5)
```

## Jarque Bera test [jb]  for GAMMA Dist

```{r gamma_jb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,JarqueBeraTest(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera Test [rjb] for GAMMA Dist

```{r gamma_rjb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,rjb.test(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kolmogorov – Smirnov test [ks] for GAMMA Dist

```{r gamma_ks, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,ks.test(rgamma(n = x, shape = 3, rate = 0.5),"pnorm"))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Shapiro-Francia method [sf] for GAMMA Dist

```{r gamma_sf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,sf.test(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Chi-square goodness of fit for normality test [gf] for GAMMA Dist

```{r gamma_gf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,PearsonTest(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Shapiro- wilk test [sw] for GAMMA Dist

```{r gamma_SW_G, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,shapiro.test(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Anderson-Darling test [AD] for GAMMA Dist

```{r gamma_AD_G, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, ad.test(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Bonett-Serial test[BS] for GAMMA Dist

```{r gamma_BS_G, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(factor(round(unlist(replicate(1000, 
                                      bonett.test(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",]), 2) 
               != round(sqrt(2/pi),  2), levels = c(TRUE, FALSE)))))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera test [RJB] for GAMMA Dist

```{r gamma_RJB_G, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, jarque.bera.test(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## D’Agostino- Pearson K2 test [DK] for GAMMA Dist

```{r gamma_DK_G, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, agostino.test(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Skewness test for GAMMA Dist

```{r gamma_SKEWNESS_G, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)
  table(abs(unlist(replicate(1000, skewness(rgamma(n = x, shape = 3, rate = 0.5))))) > 2)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kurtosis tes for GAMMA Dist

```{r gamma_KURTOSIS_G, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)
  table(replicate(1000, kurtosis(rgamma(n = x, shape = 3, rate = 0.5)))-3 > 1)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Lilliefores (LL) Test for GAMMA Dist

```{r gamma_LL_G, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, lillie.test(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Cramer–von Mises (CVM) test for GAMMA Dist

```{r gamma_CVM_G, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, cvm.test(rgamma(n = x, shape = 3, rate = 0.5)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```
######################################################################################

# UNIFORM DIST for UNIFORM Dist

```{r simulate_Uniform_Distribution, include=TRUE}
set.seed(1)
x <- runif(x)
```


## Jarque Bera test [jb]  for UNIFORM Dist

```{r unif_jb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,JarqueBeraTest(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera Test [rjb] for UNIFORM Dist

```{r unif_rjb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,rjb.test(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kolmogorov – Smirnov test [ks] for UNIFORM Dist

```{r unif_ks, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)
  table(replicate(1000,ks.test(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Shapiro-Francia method [sf] for UNIFORM Dist

```{r unif_sf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,sf.test(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Chi-square goodness of fit for normality test [gf] for UNIFORM Dist

```{r unif_gf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,PearsonTest(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```



## Shapiro- wilk test [sw] for UNIFORM Dist

```{r unif_SW_U, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,shapiro.test(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Anderson-Darling test [AD] for UNIFORM Dist

```{r unif_AD_U, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, ad.test(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Bonett-Serial test[BS] for UNIFORM Dist

```{r unif_BS_U, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(factor(round(unlist(replicate(1000, 
                                      bonett.test(runif(x)))["p.value",]), 2) 
               != round(sqrt(2/pi),  2), levels = c(TRUE, FALSE)))))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera test [RJB] for UNIFORM Dist

```{r unif_RJB_U, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, jarque.bera.test(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## D’Agostino- Pearson K2 test [DK] for UNIFORM Dist
```{r unif_DA_U, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, agostino.test(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Skewness test for UNIFORM Dist

```{r unif_SKEWNESS_U, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)   table(factor(abs(unlist(replicate(1000, skewness(runif(x))))) > 2, levels = c(TRUE, FALSE)))))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kurtosis tes for UNIFORM Dist

```{r unif_KURTOSIS_U, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)
  table(replicate(1000, kurtosis(runif(x)))-3 > 1)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Lilliefores (LL) Test for gamma for UNIFORM Dist

```{r unif_LL_U, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, lillie.test(runif(x)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```
##################################################################################################
# CHI-SQUARE DIST

```{r simulate_Chisquare_Distribution, include=TRUE}
set.seed(1)
x <- rchisq(x, df = 2)
```


## Jarque Bera test [jb]  for CHI-SQUARE Dist

```{r chisq_jb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,JarqueBeraTest(rchisq(n = x, df = 2)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera Test [rjb] for CHI-SQUARE Dist

```{r chisq_rjb, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,rjb.test(rchisq(n = x, df = 2)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kolmogorov – Smirnov test [ks] for CHI-SQUARE Dist

```{r chisq_ks, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,ks.test(rchisq(n = x, df = 2),"pnorm"))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Shapiro-Francia method [sf] for CHI-SQUARE Dist

```{r chisq_sf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,sf.test(rchisq(n = x, df = 2)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Chi-square goodness of fit for normality test [gf] for CHI-SQUARE Dist

```{r chisq_gf, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,PearsonTest(rchisq(n = x, df = 2)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```



## Shapiro- wilk test [sw] for CHI-SQUARE Dist

```{r chisq_SW_CH, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000,shapiro.test(rchisq(n = x, df = 2)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Anderson-Darling test [AD] for CHI-SQUARE Dist

```{r chisq_AD_CH, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, ad.test(rchisq(n = x, df = 2)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Bonett-Serial test[BS] for CHI-SQUARE Dist

```{r chisq_BS_CH, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(factor(round(unlist(replicate(1000, 
                                      bonett.test(rchisq(n = x, df = 2)))["p.value",]), 2) 
               != round(sqrt(2/pi),  2), levels = c(TRUE, FALSE)))))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Robust Jarque-Bera test [RJB] for CHI-SQUARE Dist

```{r chisq_RJB_CH, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, jarque.bera.test(rchisq(n = x, df = 2)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## D’Agostino- Pearson K2 test [DK] for CHI-SQUARE Dist
```{r chisq_DA_CH, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, agostino.test(rchisq(n = x, df = 2)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Skewness test for CHI-SQUARE Dist

```{r chisq_SKEWNESS_CH, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)   table(factor(abs(unlist(replicate(1000, skewness(rchisq(n = x, df = 2))))) > 2, levels = c(TRUE, FALSE)))))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Kurtosis tes for CHI-SQUARE Dist

```{r chisq_KURTOSIS_CH, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x)
  table(replicate(1000, kurtosis(rchisq(n = x, df = 2)))-3 > 1)))
row.names(out) <- c(10, 20, 50, 100)
out
```

## Lilliefores (LL) Test for gamma for CHI-SQUARE Dist

```{r chisq_LL_CH, include=TRUE}
out <- t(sapply(c(10, 20, 50, 100), function(x) 
  table(replicate(1000, lillie.test(rchisq(n = x, df = 2)))["p.value",] < 0.05)))
row.names(out) <- c(10, 20, 50, 100)
out
```


## Hypothesis Setting for Anderson-Darling Test

|   $H_0$: The data are normally distributed 

|   $H_1$: The data are not normally distributed




## Decision Rule for Anderson-Darling Test

|   Reject $H_0$: The data are normally distributed, if the the $P-Value of AD statistics is small, accept $H_1$: The data are not normally distributed otherwise.

At $5\%$ significance level

## Test Statistic: Anderson-Darling Test [AD]

```{r simm, include = TRUE}
agostino.test(x)
```

## Decision Rule for Anderson-Darling Test

Take the decision for yourself
